A self-consistency check for unitary propagation of Hawking quanta

### 2016-11-28 Draft_BH_shells.tex
1 change

The fundamental principle behind Feynman's trick is that ``classical wave coherence'',
\footnote{We remind the readers that ``coherence'' has a classical (likely original) meaning as superpositions of waves of stably similar phases.}
 in his case the observability of the interference pattern, should be taken as the prerequisite of ``quantum unitarity''. 
In Sec.\ref{sec-QFT}, we argue that this principle enables a general self-consistency check of the classical background assumption. 
We provide a natural generalization to local QFT in curved spacetime, and we discuss why such self-consistency check is different from perturbative calculations of graviton-scattering.

>>>>

The fundamental principle behind Feynman's trick is that ``classical wave coherence'',
\footnote{We remind the readers that ``coherence'' has a classical (likely original) meaning as superpositions of waves with stably similar phases.}
 in his case the observability of the interference pattern, should be taken as the prerequisite of ``quantum unitarity''. 
In Sec.\ref{sec-QFT}, we argue that this principle enables a general self-consistency check of the classical background assumption. 
We provide a natural generalization to local QFT in curved spacetime, and we discuss why such self-consistency check is different from perturbative calculations of graviton-scattering.
